\documentclass[11pt, a4paper]{letter}

\usepackage[a4paper, top=1.5cm, bottom=1.5cm, left=2.2cm, right=2.2cm]{geometry}
\usepackage{fontenc}
\usepackage{inputenc}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{hyperref}
\usepackage{xcolor}

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=blue
}

% Remove default letter formatting
\setlength{\parindent}{0pt}
\setlength{\parskip}{5pt}

\begin{document}

% ── Header ──────────────────────────────────────────────────────────────────
\begin{center}
    {\LARGE \textbf{Quoc Anh Trinh (Andrew)}}\\[4pt]
    {\small
        +61 451 886 468 \quad|\quad
        \href{mailto:andrews.trinh@gmail.com}{andrews.trinh@gmail.com} \quad|\quad
        \href{https://www.linkedin.com/in/qatrinh}{linkedin.com/in/qatrinh}
    }
\end{center}

\vspace{6pt}
\hrule
\vspace{10pt}

% ── Date & Recipient ────────────────────────────────────────────────────────
\today

\vspace{8pt}

Hiring Manager\\
Risk Analytics \& Reporting --- Group Risk\\
People First Bank

\vspace{6pt}

% ── Salutation ──────────────────────────────────────────────────────────────
Dear Hiring Manager,

% ── Opening ─────────────────────────────────────────────────────────────────
I am writing to apply for the newly created \textbf{Risk Analytics \& AI} role within People First Bank's Group Risk team, reporting to the Head of Risk Analytics \& Reporting. Over five years in Australian banking and FinTech --- currently leading the Intelligence and Analytics function within Financial Crime Risk at Bendigo \& Adelaide Bank --- I have delivered exactly the analytics, automation and AI-enabled capability this role is designed to drive, working at the intersection of risk, data and emerging technology that this position sits squarely within.

% ── Why People First Bank ───────────────────────────────────────────────────
What draws me to People First Bank is the chance to help define a brand-new capability at a values-driven mutual that is big enough to make an impact yet agile enough to do genuinely interesting work --- shaping how AI, automation and advanced analytics strengthen risk capability across the Bank from the ground up.

% ── Core achievements ───────────────────────────────────────────────────────
\textbf{AI and agents:}
I co-designed an end-to-end AI-driven UAR-to-SMR regulatory reporting pipeline using LLMs, NLP, Python and SQL --- with secure data masking and validated prompting --- cutting reporting preparation time by \textbf{80\%}. I have also built production agentic AI solutions (enforcement-action checkers and typology extractors on FastAPI/GCP with vector search), the same agent-building discipline behind MS Copilot and Databricks, with hands-on Spark/PySpark that translates directly to a Databricks lakehouse.

\textbf{Dashboards and process automation:}
I own the Power BI dashboards in our transaction monitoring product, eliminating \textbf{70\%} of ad-hoc requests and cutting prioritisation time by \textbf{60\%}, and built automated daily workflows processing \textbf{150+} alerts at \textbf{99.9\%} integrity --- practical automation I am keen to extend across the Power Platform's BI, Automate and Apps.

\textbf{Risk, governance and process improvement:}
Working across financial crime risk, compliance and assurance, I embed governance and controls into emerging-technology and AI solutions --- including the privacy and transparency controls built into my LLM pipelines. I led the annual monitoring performance review using statistical calibration to remove \textbf{5{,}000+} unnecessary alerts and save \textbf{300+} hours a year, and engineered interim SQL monitoring that held \textbf{100\%} compliance continuity across \textbf{2M+} transactions during a platform exit.

% ── Research / broader credentials ──────────────────────────────────────────
I am also beginning a formal research journey on a topic closely aligned with this role --- \textbf{AI for compliance} --- reflecting how seriously I take both the opportunity and responsibility of bringing AI into regulated risk work. Alongside my \textbf{Master of Business Analytics from Deakin University}, I enjoy being a trusted advisor and champion of innovation, and bring genuine facilitation strength, having tutored over \textbf{100 students} in SQL and Python.

% ── Closing ─────────────────────────────────────────────────────────────────
I would welcome the opportunity to discuss how my background can help People First Bank build its future risk-analytics and AI capability. My resume is attached, and I am available at your convenience.

Thank you for considering my application.

\vspace{6pt}

Warm regards,

\vspace{18pt}

\textbf{Quoc Anh Trinh (Andrew)}\\
+61 451 886 468\\
\href{mailto:andrews.trinh@gmail.com}{andrews.trinh@gmail.com}\\
\href{https://www.linkedin.com/in/qatrinh}{linkedin.com/in/qatrinh}

\end{document}
