\documentclass[11pt, a4paper]{article}

\usepackage[a4paper, top=2cm, bottom=2cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=blue
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{8pt}

\pagestyle{empty}

\begin{document}

% ── Header ──────────────────────────────────────────────────────────────────
\begin{center}
    {\LARGE \textbf{Quoc Anh Trinh (Andrew)}}\\[4pt]
    {\small
        +61 451 886 468 \quad|\quad
        \href{mailto:andrews.trinh@gmail.com}{andrews.trinh@gmail.com} \quad|\quad
        \href{https://www.linkedin.com/in/qatrinh}{linkedin.com/in/qatrinh}
    }
\end{center}

\vspace{4pt}
\hrule
\vspace{14pt}

% ── Date ────────────────────────────────────────────────────────────────────
\today

\vspace{8pt}

Hiring Manager\\
Systematic Equities Team\\
AustralianSuper

\vspace{10pt}

% ── Salutation ──────────────────────────────────────────────────────────────
Dear Hiring Manager,

% ── Opening ─────────────────────────────────────────────────────────────────
I am writing to express my strong interest in the \textbf{Analyst (Systematic Equities)} position at AustralianSuper. With a Master of Business Analytics and over five years of experience in leading data-driven functions within the Australian banking sector, I am drawn to this role because of the opportunity to apply software engineering and quantitative research to deliver superior outcomes for your millions of members. I thrive at the intersection of complex financial data management and production-quality code.

% ── Why AustralianSuper ─────────────────────────────────────────────────────
AustralianSuper’s reputation for supporting member-first outcomes through a high-performance environment underpinned by a strong risk culture deeply resonates with my professional values. I am particularly attracted to the Systematic Equities team's focus on managing diverse listed equity strategies and the strategic goal of reducing external management costs. I am eager to contribute to a team that values both technical rigour and the diverse needs of its colleagues.

% ── Core experience tailored to Systematic Equities ────────────────────────
In my current role as Lead of Intelligence and Analytics at Bendigo \& Adelaide Bank, I manage the full data lifecycle for complex, large-scale datasets. My experience aligns directly with the "Analyst" requirements:

\textbf{Advanced Data Management and Ingestion:}
I have extensive experience working with "dirty" and complex datasets. I have designed and executed robust data processes for the ingestion and transformation of millions of transactions, ensuring 99.9\% data integrity across vendor-agnostic pipelines. I am adept at identifying data quality issues and building automated tools to mitigate them, which is essential for ensuring the reliability of financial markets data used in research and trading.

\textbf{Engineering Python and SQL Solutions:}
I apply Python and SQL daily with a focus on data science and best practices. I am well-versed in version control, unit testing, and code optimisation—essential skills for maintaining a production-ready quant codebase. My achievements include co-designing and automating regulated reporting pipelines that reduced prep time by 80\%, demonstrating my ability to automate day-to-day activities while maintaining high standards of software engineering.

\textbf{Risk Culture and Governance:}
Coming from a Financial Crime Risk background, an obsession with risk controls and adherence to policies is in my DNA. I understand the importance of implementing strong controls on processes, systems, and workflows to ensure adherence to organisational standards. I am comfortable working in and administering cloud environments (AWS/GCP), which supports both the scale and security required for institutional funds management.

\textbf{Collaboration and Communication:}
I have a proven history of partnering with operational, investment, and IT teams to translate complex business needs into technical solutions. Whether dealing with internal stakeholders or external data vendors, I pride myself on delivering clear, decision-ready insights and fostering a collaborative environment.

% ── Closing ─────────────────────────────────────────────────────────────────
I am genuinely excited about the prospect of bringing my technical expertise in data engineering and my passion for quantitative analysis to the Systematic Equities team. I look forward to discussing how my background in financial data and software engineering can support AustralianSuper’s mission.

Thank you for your time and consideration.

\vspace{20pt}

Warm regards,

\vspace{30pt}

\textbf{Quoc Anh Trinh (Andrew)}\\
+61 451 886 468\\
\href{mailto:andrews.trinh@gmail.com}{andrews.trinh@gmail.com}\\
\href{https://www.linkedin.com/in/qatrinh}{linkedin.com/in/qatrinh}

\end{document}
