\documentclass[11pt, a4paper]{article}

\usepackage[a4paper, top=2cm, bottom=2cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=blue
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{8pt}

\pagestyle{empty}

\begin{document}

% ── Header ──────────────────────────────────────────────────────────────────
\begin{center}
    {\LARGE \textbf{Quoc Anh Trinh (Andrew)}}\\[4pt]
    {\small
        +61 451 886 468 \quad|\quad
        \href{mailto:andrews.trinh@gmail.com}{andrews.trinh@gmail.com} \quad|\quad
        \href{https://www.linkedin.com/in/qatrinh}{linkedin.com/in/qatrinh}
    }
\end{center}

\vspace{4pt}
\hrule
\vspace{14pt}

% ── Date ────────────────────────────────────────────────────────────────────
\today

\vspace{8pt}

Hiring Manager\\
Data, Analytics \& Insights Team\\
UniSuper

\vspace{10pt}

% ── Salutation ──────────────────────────────────────────────────────────────
Dear Hiring Manager,

% ── Opening ─────────────────────────────────────────────────────────────────
I am writing to apply for the \textbf{Senior Data Analyst} role within UniSuper's data, analytics and insights function. With over five years of experience as a data analyst in financial services --- specialising in Power BI, SQL, Python, and cloud-based analytics --- I am drawn to this role because of the purpose it serves: helping Australians achieve great retirement outcomes through trusted, high-quality data.

% ── Why UniSuper ─────────────────────────────────────────────────────────────
UniSuper's position as one of Australia's most respected superannuation funds, managing over \$139 billion on behalf of its members, reflects an organisation that takes its responsibilities seriously. I am particularly attracted to a culture built on genuine care, collaboration, and a passion for outcomes --- values that resonate with how I approach my work. The opportunity to contribute to an Enterprise Data Platform and help mature self-service analytics capabilities across a complex, member-focused organisation is exactly the kind of challenge I am looking for.

% ── Core experience ──────────────────────────────────────────────────────────
In my current role at Bendigo \& Adelaide Bank, I lead the intelligence and analytics function within Financial Crime Risk, working across the full data lifecycle from requirements translation through to stakeholder-facing insights. My experience maps directly to what UniSuper is seeking:

\textbf{Power BI design and delivery:}
I design, build, and maintain Power BI dashboards serving operations, transformation, and governance stakeholders. My dashboards eliminated 70\% of ad-hoc reporting requests and reduced prioritisation time by 60\% --- outcomes that required both strong technical execution and an understanding of what business users actually need.

\textbf{SQL and Python proficiency:}
I apply SQL and Python daily to build complex datasets, engineer automated workflows, and solve problems that span both analytics and data engineering. This includes vendor-agnostic transaction monitoring scenarios processing 150+ alerts daily with 99.9\% data integrity, and automated reporting pipelines using NLP and LLMs that reduced regulatory preparation time by 80\%.

\textbf{Translating business needs into data solutions:}
I work closely with compliance, operations, and assurance stakeholders to understand requirements and turn them into scalable, reusable data assets. I have also contributed to data model design and supported assurance testing of 40+ scenarios during a major bank migration --- requiring close coordination with both business and technical teams.

\textbf{Promoting data literacy and self-service:}
Beyond my core role, I have tutored over 100 students in SQL and Python, and I take a deliberate approach to building analytical capability in those around me. Helping non-technical stakeholders interpret and trust data is something I find genuinely rewarding.

\textbf{Financial services experience:}
My experience at Bendigo \& Adelaide Bank and Remitano (an international cryptocurrency exchange) has given me strong grounding in financial data environments --- where accuracy, auditability, and stakeholder trust are non-negotiable. While my background is in banking rather than superannuation, the data challenges --- regulated reporting, member-level analysis, performance monitoring --- are closely aligned.

% ── Qualifications ───────────────────────────────────────────────────────────
I hold a \textbf{Master of Business Analytics from Deakin University} and have hands-on experience with cloud platforms including AWS (Redshift, Glue) and exposure to Azure-based tooling. I am actively building familiarity with Databricks and the broader Azure data ecosystem, which I understand is part of UniSuper's platform direction.

% ── Closing ─────────────────────────────────────────────────────────────────
I am genuinely excited about the opportunity to contribute to UniSuper's data and analytics journey --- not just as a technical practitioner, but as someone who believes that better data leads to better decisions and, ultimately, better outcomes for members. I would welcome the opportunity to discuss how my background can support your team.

Thank you for considering my application. I am available at your convenience for an interview.

\vspace{20pt}

Warm regards,

\vspace{30pt}

\textbf{Quoc Anh Trinh (Andrew)}\\
+61 451 886 468\\
\href{mailto:andrews.trinh@gmail.com}{andrews.trinh@gmail.com}\\
\href{https://www.linkedin.com/in/qatrinh}{linkedin.com/in/qatrinh}

\end{document}