\documentclass[11pt, a4paper]{letter}

\usepackage[a4paper, top=2cm, bottom=2cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage{fontenc}
\usepackage{inputenc}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{hyperref}
\usepackage{xcolor}

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=blue
}

% Remove default letter formatting
\setlength{\parindent}{0pt}
\setlength{\parskip}{8pt}

\begin{document}

% ── Header ──────────────────────────────────────────────────────────────────
\begin{center}
    {\LARGE \textbf{Quoc Anh Trinh (Andrew)}}\\[4pt]
    {\small
        +61 451 886 468 \quad|\quad
        \href{mailto:andrews.trinh@gmail.com}{andrews.trinh@gmail.com} \quad|\quad
        \href{https://www.linkedin.com/in/qatrinh}{linkedin.com/in/qatrinh}
    }
\end{center}

\vspace{6pt}
\hrule
\vspace{14pt}

% ── Date & Recipient ────────────────────────────────────────────────────────
\today

\vspace{8pt}

Hiring Manager\\
Group Risk Team\\
People First Bank

\vspace{10pt}

% ── Salutation ──────────────────────────────────────────────────────────────
Dear Hiring Manager,

% ── Opening ─────────────────────────────────────────────────────────────────
I am writing to apply for the \textbf{Risk Analytics \& AI Enablement Specialist} role within People First Bank's Group Risk team. With over five years of data analytics experience in Australian banking and FinTech --- including my current role at Bendigo \& Adelaide Bank --- I bring a proven track record of delivering exactly the kind of data-driven, AI-powered risk solutions this role calls for.

% ── Why People First Bank ───────────────────────────────────────────────────
What draws me to People First Bank is the purpose behind the work. As Australia's leading mutual bank serving over 700,000 members, People First Bank is building something genuinely different --- a modern, digital-first institution with deep community roots and a vision to deliver positive change through banking. I am particularly energised by the bank's current phase of technology investment and the ambition to bring innovation into risk management in a meaningful way. That ambition aligns closely with the work I have been doing and the direction I want to take my career.

% ── Core achievements ───────────────────────────────────────────────────────
In my current role leading the Intelligence and Analytics function within Financial Crime Risk, I have built and delivered solutions across the full spectrum of what this role requires:

\textbf{Data analytics and dashboarding:}
I designed and maintain Power BI dashboards that eliminated 70\% of ad-hoc reporting requests and reduced alert prioritisation time by 60\%, directly serving operations, transformation, and governance teams --- the same stakeholder landscape this role involves.

\textbf{AI and automation:}
I co-designed and automated the UAR-to-SMR regulatory reporting pipeline using Large Language Models, NLP, Python, and SQL --- reducing reporting preparation time by 80\%. I also built an AI-driven typology and indicator management platform that extracted and structured 156 AUSTRAC documents into 198 actionable typologies and 300+ indicators, forming the foundation for a modern data-led monitoring framework.

\textbf{SQL and Python proficiency:}
From engineering vendor-agnostic transaction monitoring scenarios processing 150+ daily alerts with 99.9\% data integrity, to building automated workflows that replaced manual transfers entirely, I apply coding to solve real operational problems --- not just analyse them.

\textbf{Risk domain experience:}
Having worked within financial crime risk, compliance, and assurance at a major Australian bank, I understand the stakes of getting risk analytics right. I have led annual performance reviews using statistical calibration to reduce false positives and remove unnecessary alerts, saving over 300 investigation hours annually.

\textbf{Process improvement and transition support:}
I led the engineering of interim SQL-based monitoring during Bendigo Bank's exit from its legacy platform, maintaining 100\% compliance continuity across 2 million+ transactions --- exactly the kind of BAU-critical, high-stakes delivery this role will involve.

% ── Broader credentials ─────────────────────────────────────────────────────
I am genuinely curious about emerging technology and actively apply it: I have worked with LLMs, vector databases, agentic AI pipelines, AWS Glue, and Redshift in production environments. I hold a \textbf{Master of Business Analytics from Deakin University} and complement my formal qualifications with continuous self-directed learning and practical application --- including tutoring over 100 students in SQL and Python and winning two GovHack hackathon prizes.

% ── Closing ─────────────────────────────────────────────────────────────────
I would welcome the opportunity to discuss how my background can support People First Bank's Group Risk team. Please find my resume attached. I am available at your convenience for an interview.

Thank you for considering my application.

\vspace{20pt}

Warm regards,

\vspace{30pt}

\textbf{Quoc Anh Trinh (Andrew)}\\
+61 451 886 468\\
\href{mailto:andrews.trinh@gmail.com}{andrews.trinh@gmail.com}\\
\href{https://www.linkedin.com/in/qatrinh}{linkedin.com/in/qatrinh}

\end{document}