\documentclass[11pt, a4paper]{article}

\usepackage[a4paper, top=2cm, bottom=2cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=blue
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{8pt}

\pagestyle{empty}

\begin{document}

% ── Header ──────────────────────────────────────────────────────────────────
\begin{center}
    {\LARGE \textbf{Quoc Anh Trinh (Andrew)}}\\[4pt]
    {\small
        +61 451 886 468 \quad|\quad
        \href{mailto:andrews.trinh@gmail.com}{andrews.trinh@gmail.com} \quad|\quad
        \href{https://www.linkedin.com/in/qatrinh}{linkedin.com/in/qatrinh}
    }
\end{center}

\vspace{4pt}
\hrule
\vspace{14pt}

% ── Date ────────────────────────────────────────────────────────────────────
\today

\vspace{8pt}

Hiring Manager\\
Data and Analytics Division\\
Tertiary Education Data Asset

\vspace{10pt}

% ── Salutation ──────────────────────────────────────────────────────────────
Dear Hiring Manager,

% ── Opening ─────────────────────────────────────────────────────────────────
I am writing to express my strong interest in the \textbf{Senior Data Scientist / Lead Data Analyst} role. With over five years of experience in leading advanced analytical functions and a Master of Business Analytics, I am excited by the opportunity to lead the delivery of the national-scale tertiary education data asset. My background in engineering robust administrative data pipelines and applying econometric methods within highly regulated financial environments position me well to provide the technical leadership and strategic oversight this role requires.

% ── Core experience tailored to the role ───────────────────────────────────
In my current capacity as Lead of Intelligence and Analytics at Bendigo \& Adelaide Bank, I manage the end-to-end data lifecycle for sensitive financial crime datasets. My experience directly maps to the key requirements of your team:

\textbf{Leading Administrative Data Engineering:}
I have a proven track record of designing and sustaining complex data pipelines from ingestion through to publication. I led the establishment of automated regulated reporting pipelines using Python, SQL, and NLP that reduced preparation time by 80\% while ensuring 99.9\% data integrity. I am adept at managing large-scale administrative datasets and implementing performance-optimised architectures that survive rigorous audit and governance standards.

\textbf{Advanced Statistical and Econometric Expertise:}
Beyond technical engineering, I apply advanced econometric and causal inference methods to evaluate system performance. In my work with transaction monitoring, I utilised statistical calibration and trend modelling to achieve 60-70\% true positive rates, saving thousands of investigation hours. My academic foundation in Business Analytics from Deakin University included deep exposure to statistical modelling, which I apply daily to deliver evidence-based insights that inform executive-level decision-making.

\textbf{Governance of Sensitive Data Assets:}
Working in financial services has instilled a fundamental commitment to data security and privacy. I have extensive experience governing sensitive datasets where confidentiality is non-negotiable. I am eligible for and ready to undergo the process for a Baseline Security Clearance, and I am well-versed in establishing reproducibility and validation standards that ensure analytical products are trusted and scalable.

\textbf{Technical Leadership and Mentorship:}
I am a dedicated mentor who believes in uplifting team capability. I have personally tutored over 100 students in SQL and Python, and in my professional roles, I take a proactive approach to guiding analytical standards and developing the next generation of data scientists. I am comfortable providing strategic advice to senior stakeholders, translating "black-box" models into clear, decision-ready briefings.

% ── Closing ─────────────────────────────────────────────────────────────────
I am genuinely motivated by the prospect of applying my skills in Python, R, and SQL to a mission as critical as tertiary education performance. I thrive in policy-intensive environments where technical rigour meets high-impact delivery, and I would welcome the opportunity to discuss how my experience can support your division’s goals.

Thank you for your time and consideration.

\vspace{20pt}

Warm regards,

\vspace{30pt}

\textbf{Quoc Anh Trinh (Andrew)}\\
+61 451 886 468\\
\href{mailto:andrews.trinh@gmail.com}{andrews.trinh@gmail.com}\\
\href{https://www.linkedin.com/in/qatrinh}{linkedin.com/in/qatrinh}

\end{document}
