\documentclass[11pt, a4paper]{article}

\usepackage[a4paper, top=2cm, bottom=2cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=blue
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{8pt}

\pagestyle{empty}

\begin{document}

% ── Header ──────────────────────────────────────────────────────────────────
\begin{center}
    {\LARGE \textbf{Quoc Anh Trinh (Andrew)}}\\[4pt]
    {\small
        +61 451 886 468 \quad|\quad
        \href{mailto:andrews.trinh@gmail.com}{andrews.trinh@gmail.com} \quad|\quad
        \href{https://www.linkedin.com/in/qatrinh}{linkedin.com/in/qatrinh}
    }
\end{center}

\vspace{4pt}
\hrule
\vspace{14pt}

% ── Date ────────────────────────────────────────────────────────────────────
\today

\vspace{8pt}

Hiring Manager\\
Data Science Team\\
HESTA

\vspace{10pt}

% ── Salutation ──────────────────────────────────────────────────────────────
Dear Hiring Manager,

% ── Opening ─────────────────────────────────────────────────────────────────
I am writing to express my enthusiastic interest in the \textbf{Data Scientist} position at HESTA. As a purpose-driven analytics leader with a Master of Business Analytics and a proven track record in deploying Generative AI and machine learning solutions, I am inspired by HESTA’s mission to deliver better retirement outcomes for members with real-world impact. I thrive at the intersection of cutting-edge technology and meaningful social purpose, making this 12-month opportunity a natural fit for my skills and values.

% ── AI Innovation & Technical Excellence ───────────────────────────────────
In my current role as Lead of Intelligence and Analytics at Bendigo \& Adelaide Bank, I have been driving AI innovation through end-to-end data science products. My experience directly aligns with HESTA’s key objectives:

\textbf{Driving AI and Generative AI Innovation:}
I have successfully leveraged LLMs and NLP to solve complex business problems, notably co-designing an automated regulatory reporting pipeline that reduced preparation time by 80\%. I am comfortable maintaining traditional predictive models while simultaneously exploring the frontiers of Generative AI to uncover patterns and opportunities that enhance organisational performance.

\textbf{Building Production-Grade Solutions:}
I have deep experience deploying scalable, end-to-end solutions from concept to production. I apply modern software development practices—including Git, Docker, and CI/CD—to ensure that data delivery solutions are robust and reproducible. My background in developing cloud-based processes (GCP and AWS) ensures I can contribute effectively to your infrastructure-as-code initiatives.

\textbf{Actionable Insights and Stakeholder Partnering:}
I believe that technical excellence is only as valuable as its ability to inform decision-making. I have a long-standing commitment to "communication excellence," having tutored over 100 students in SQL and Python and frequently presenting "executive-ready" briefings to senior stakeholders. I excel at translating complex technical findings into clear recommendations that support evidence-based decision frameworks.

% ── Why HESTA & Sector Fit ──────────────────────────────────────────────────
Having spent over five years in the Australian financial services sector, I understand the unique responsibility of protecting and growing members' wealth. I am an advocate for inclusion and collaboration, and I am proactive in managing risk—a trait honed in my current role within Financial Crime Risk. I am eager to apply my technical rigour and "AI-first" mindset to support HESTA's diverse community of more than one million members.

% ── Closing ─────────────────────────────────────────────────────────────────
I am ready to step into this role and make an immediate impact on your data-led decision-making capability. I look forward to the opportunity to discuss how my background in finance, AI innovation, and robust engineering can support HESTA’s mission.

Thank you for your time and consideration.

\vspace{20pt}

Warm regards,

\vspace{30pt}

\textbf{Quoc Anh Trinh (Andrew)}\\
+61 451 886 468\\
\href{mailto:andrews.trinh@gmail.com}{andrews.trinh@gmail.com}\\
\href{https://www.linkedin.com/in/qatrinh}{linkedin.com/in/qatrinh}

\end{document}
