\documentclass[11pt, a4paper]{article}

\usepackage[a4paper, top=2cm, bottom=2cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=blue
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{8pt}

\pagestyle{empty}

\begin{document}

% ── Header ──────────────────────────────────────────────────────────────────
\begin{center}
    {\LARGE \textbf{Quoc Anh Trinh (Andrew)}}\\[4pt]
    {\small
        +61 451 886 468 \quad|\quad
        \href{mailto:andrews.trinh@gmail.com}{andrews.trinh@gmail.com} \quad|\quad
        \href{https://www.linkedin.com/in/qatrinh}{linkedin.com/in/qatrinh}
    }
\end{center}

\vspace{4pt}
\hrule
\vspace{14pt}

% ── Date ────────────────────────────────────────────────────────────────────
\today

\vspace{8pt}

Hiring Manager\\
Data \& Technology Team\\
Liberty Financial

\vspace{10pt}

% ── Salutation ──────────────────────────────────────────────────────────────
Dear Hiring Manager,

% ── Opening ─────────────────────────────────────────────────────────────────
I am writing to apply for the data engineering position within Liberty’s Data \& Technology team. As a professional who thrives in "free-thinking" environments and possesses a Master of Business Analytics, I am excited by Liberty’s "AI-first" data platform direction. My experience building production-grade Python services, managing cloud infrastructure, and delivering curated data layers for both BI and AI outcomes makes me a strong fit for your modern Microsoft Fabric and Azure stack.

% ── Why Liberty & Values ───────────────────────────────────────────────────
Liberty’s reputation as a challenger in the lending space, driven by the FLAIR values, deeply resonates with my professional ethos. I am particularly drawn to the focus on being "Resourceful" and "Learning" — values that are essential when working at the bleeding edge of AI-assisted development and cloud-native data platforms. I am eager to contribute to a collaborative community that champions flexible financial solutions through exceptional digital experiences.

% ── Core experience tailored to Liberty ────────────────────────────────────
In my current role at Bendigo \& Adelaide Bank, I lead the intelligence and analytics function within Financial Crime Risk. My technical background aligns directly with what Liberty is building:

\textbf{Production-Grade Data Pipelines and Python Services:}
I have extensive experience designing and deploying automated workflows and Python-based services. I am comfortable working with the Medallion architecture (Bronze $\rightarrow$ Silver $\rightarrow$ Gold) to create reliable, curated data layers. My work includes building vendor-agnostic pipelines that process 150+ alerts daily with 99.9\% data integrity, ensuring that data is not just available, but production-ready and high-quality.

\textbf{AI-First Mindset and Intelligent Services:}
I am passionate about empowering AI workloads. At Bendigo, I developed automated reporting pipelines using NLP and LLMs that reduced regulatory preparation time by 80\%. I understand the intricacies of powering intelligent services like speech-to-text and NLP through well-modelled data, and I am excited by the prospect of deploying these services onto modern stacks like Azure Kubernetes Service (AKS).

\textbf{Infrastructure, CI/CD, and Clean Code:}
I value strong engineering practices, including infrastructure as code (Terraform) and robust CI/CD pipelines. I believe that data quality is sustained through automated testing, monitoring, and observability. My approach combines technical rigour with a drive for "clean code" that ensures scalability and reproducibility across the full data lifecycle.

\textbf{Stakeholder Collaboration and Business Impact:}
I thrive on translating complex business goals into technical solutions. Whether collaborating with Risk, Data Science, or Technology teams, I focus on delivering data products that drive actual decisions. My work building Power BI dashboards has historically reduced ad-hoc reporting requests by 70\%, demonstrating my ability to deliver platform-level value that empowers self-service and discoverability.

% ── Qualifications and Growth ──────────────────────────────────────────────
With a \textbf{Master of Business Analytics from Deakin University} and hands-on experience in AWS and Azure environments, I am a fast learner who enjoys working across domains. While I am already proficient in SQL and Python, I am eager to further specialise in Microsoft Fabric and AI-assisted development as part of Liberty’s forward-thinking team.

% ── Closing ─────────────────────────────────────────────────────────────────
I am impressed by Liberty's commitment to building a social and collaborative community, and I am more than happy to support this through the three-day in-office requirement. I look forward to the opportunity to discuss how my "FLAIR" for data engineering can help shape the future of Liberty’s AI-first platform.

Thank you for considering my application.

\vspace{20pt}

Warm regards,

\vspace{30pt}

\textbf{Quoc Anh Trinh (Andrew)}\\
+61 451 886 468\\
\href{mailto:andrews.trinh@gmail.com}{andrews.trinh@gmail.com}\\
\href{https://www.linkedin.com/in/qatrinh}{linkedin.com/in/qatrinh}

\end{document}
