\documentclass[11pt, a4paper]{article}

\usepackage[a4paper, top=2cm, bottom=2cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}

\begin{document}

\begin{flushleft}
\textbf{Quoc Anh Trinh (Andrew)} \\
Melbourne, Victoria \\
+61 451 886 468 \\
\href{mailto:andrews.trinh@gmail.com}{andrews.trinh@gmail.com} \\
\href{https://www.linkedin.com/in/qatrinh/}{linkedin.com/in/qatrinh} \\
\vspace{1em}
\today
\end{flushleft}

\vspace{1em}

\begin{flushleft}
\textbf{To the Uniware Hiring Team,}
\end{flushleft}

\vspace{1em}

I was particularly excited to see the Software Engineer – AWS DevOps role at Uniware Managed Services, especially the emphasis on \textbf{AI-assisted development}. As a builder who has integrated AI-assisted coding tools into my daily workflow for over 18 months, I have experienced firsthand how these tools accelerate the delivery of robust, production-grade cloud software.

In my current tenure at Bendigo \& Adelaide Bank, I leverage AI agents to architect and deploy complex data solutions within regulated banking environments. My background aligns directly with Uniware's core requirements:

\begin{itemize}
    \item \textbf{AI-Assisted Development:} I use generative AI for everything from initial architectural scaffolding to complex debugging and unit test generation. This practice enabled me to co-design and deliver an \textbf{AI-driven UAR-to-SMR pipeline} implementing secure \textbf{data masking/rehydration} and \textbf{Pydantic-validated LLM prompting}; this reduced regulatory reporting preparation time by \textbf{80\%}, shifting the team's focus to high-value analysis.
    \item \textbf{AWS \& Cloud Operations:} I have extensive experience building scalable pipelines using \textbf{AWS Glue} and \textbf{Redshift}, and recently architected a multi-tenant platform using \textbf{FastAPI} and \textbf{Next.js} on \textbf{GCP}. My work involves building vendor-agnostic scenarios and automated daily workflows that process 150+ alerts with \textbf{99.9\% integrity}, demonstrating my comfort with secure, modern DevOps practices.
    \item \textbf{Python \& API Design:} I specialize in designing Python-based API services and \textbf{Agentic AI solutions}. I recently engineered a typology extractor that transformed 156 complex AUSTRAC documents into structured data, establishing high-performance governance for national monitoring.
\end{itemize}

Uniware’s focus on leveraging cutting-edge tools to drive ERP, WMS, and Ecommerce platforms matches my ambition to build software that is not just functional, but intelligent. My experience in financial crime risk has instilled a "security-first" mindset, ensuring that the automations and cloud infrastructures I build are as resilient as they are efficient.

I am eager to bring my unique combination of AWS/Python proficiency and advanced AI-assisted development skills to the Uniware team. Thank you for your time and consideration. I look forward to discussing how I can help shape the next generation of intelligent software solutions at Paperless Warehousing.

\vspace{2em}

Sincerely,

\vspace{1em}

Quoc Anh Trinh (Andrew)

\end{document}
