\documentclass[11pt, a4paper]{article}

\usepackage[a4paper, top=2cm, bottom=2cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=blue
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{8pt}

\pagestyle{empty}

\begin{document}

% ── Header ──────────────────────────────────────────────────────────────────
\begin{center}
    {\LARGE \textbf{Quoc Anh Trinh (Andrew)}}\\[4pt]
    {\small
        +61 451 886 468 \quad|\quad
        \href{mailto:andrews.trinh@gmail.com}{andrews.trinh@gmail.com} \quad|\quad
        \href{https://www.linkedin.com/in/qatrinh}{linkedin.com/in/qatrinh}
    }
\end{center}

\vspace{4pt}
\hrule
\vspace{14pt}

% ── Date ────────────────────────────────────────────────────────────────────
\today

\vspace{8pt}

Hiring Manager\\
Enterprise AI Squad\\
Australian Unity

\vspace{10pt}

% ── Salutation ──────────────────────────────────────────────────────────────
Dear Hiring Manager,

% ── Opening ─────────────────────────────────────────────────────────────────
I am writing to express my strong interest in the \textbf{Senior AI Enablement Engineer} position at Australian Unity. As a technical leader with a Master of Business Analytics and deep experience in deploying AI solutions within highly regulated environments, I am excited by the prospect of helping Australian Unity become an AI-native enterprise. I thrive at the intersection of complex technical engineering and product-style delivery—translating real-world business needs into high-impact, transparent, and fair AI outcomes.

% ── AI/LLM Experience & Product Mindset ─────────────────────────────────────
In my current role as Lead of Intelligence and Analytics at Bendigo \& Adelaide Bank, I have spent the last five years delivering end-to-end AI and analytics products. My background aligns directly with the "product-oriented" technologist profile you are seeking:

\textbf{Practical AI/LLM Implementation:}
I have hands-on experience applying LLM and NLP technologies to solve high-stakes business problems. I recently co-designed an automated regulatory reporting pipeline using LLMs, which reduced preparation time by 80\% while maintaining 99.9\% data integrity. This required me to move beyond simple technical execution—identifying the opportunity, shaping requirements, and managing the solution through to delivery and post-launch support.

\textbf{Governance, Fairness, and Risk-Awareness:}
Working in Financial Crime Risk has made me a "risk control-first" engineer. I have deep experience evaluating model behaviour, reducing false positives, and ensuring that automated detection scenarios align with strict fairness and transparency standards. I am comfortable challenging assumptions—whether from internal stakeholders or external vendors—to ensure that AI models meet rigorous compliance and performance benchmarks.

\textbf{Translation and AI Literacy:}
As a Deakin University alumnus who has tutored over 100 students in Python and SQL, I pride myself on my ability to simplify complex AI concepts for non-technical audiences. I understand that AI adoption is as much about human confidence and literacy as it is about technical performance. I am eager to contribute to Australian Unity's AI literacy and change initiatives, building confidence within the People \& Culture function.

% ── Closing ─────────────────────────────────────────────────────────────────
I am drawn to Australian Unity’s commitment to well-being and community, values that resonate with my own approach to ethical AI development. I am excited by the freedom this role offers to shape the evolution of enterprise-level AI practices. I look forward to the possibility of discussing how my blend of hands-on AI engineering and product-driven leadership can deliver measurable value to your business squads.

Thank you for your time and consideration.

\vspace{20pt}

Warm regards,

\vspace{30pt}

\textbf{Quoc Anh Trinh (Andrew)}\\
+61 451 886 468\\
\href{mailto:andrews.trinh@gmail.com}{andrews.trinh@gmail.com}\\
\href{https://www.linkedin.com/in/qatrinh}{linkedin.com/in/qatrinh}

\end{document}
