\documentclass[11pt, a4paper]{article}

\usepackage[a4paper, top=2cm, bottom=2cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=blue
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}

\pagestyle{empty}

\begin{document}

% ── Header ──────────────────────────────────────────────────────────────────
\begin{center}
    {\LARGE \textbf{Quoc Anh Trinh (Andrew)}}\\[4pt]
    {\small
        +61 451 886 468 \quad|\quad
        \href{mailto:andrews.trinh@gmail.com}{andrews.trinh@gmail.com} \quad|\quad
        \href{https://www.linkedin.com/in/qatrinh}{linkedin.com/in/qatrinh}
    }
\end{center}

\vspace{4pt}
\hrule
\vspace{14pt}

% ── Date ────────────────────────────────────────────────────────────────────
\today

\vspace{8pt}

Hiring Manager\\
Financial Crime Detection\\
Westpac Group

\vspace{10pt}

% ── Salutation ──────────────────────────────────────────────────────────────
Dear Hiring Manager,

% ── Opening ─────────────────────────────────────────────────────────────────
I am writing to express my strong interest in the \textbf{Senior Analyst -- Transaction Monitoring \& Analytics} role within Westpac's Financial Crime Detection function. I currently own the transaction monitoring analytics function in the Financial Crime Risk unit at Bendigo \& Adelaide Bank, where my work centres on exactly what this role describes: sharpening detection rules, improving data quality, and building analytics pipelines that turn business and regulatory needs into risk-based outcomes. Strengthening financial crime detection through advanced analytics is precisely the work I want to keep doing, and to do at greater scale.

% ── Detection rules & analytics ──────────────────────────────────────────────
Improving and supporting detection rules is the core of my current role. I researched and designed \textbf{9 new} detection scenarios and fine-tuned monitoring for Child Exploitation, Sextortion, Drug Trafficking, and Terrorism Financing typologies—using statistical calibration, genetic algorithms, and trend modelling to reach \textbf{60--70\% true positive rates} while cutting alert volume by \textbf{67\%}. My annual review of the scenario suite applied confidence testing and SQL-based recalibration to remove \textbf{5,000+ unnecessary alerts a year}, saving over \textbf{300 investigation hours}—continuous, risk-based optimisation of a live TM environment.

% ── Data pipelines & data quality ────────────────────────────────────────────
I also have deep hands-on experience across large, complex datasets and the pipelines that feed them. I built SQL- and Python-based scenarios outside vendor platforms with automated daily workflows processing \textbf{150+ alerts a day at 99.9\% data integrity}, and engineered an interim monitoring function that held \textbf{100\% continuity across 2M+ transactions} with zero compliance breaches during a core-system transition. My primary stack is advanced SQL and Python; while my recent pipeline work has been on BigQuery and dbt rather than SAS and Teradata, I ramp quickly on new data platforms and would apply the same rigour to Westpac's TM environment.

% ── Stakeholder engagement ───────────────────────────────────────────────────
Just as important is translating technical work for the people who act on it. I own the Power BI dashboards for our transaction monitoring product—delivering the KPIs, guardrails, and measures that operations, compliance, assurance, and governance teams rely on, which removed \textbf{70\%} of recurring ad-hoc requests. I work across cross-functional teams daily and take accountability for delivery: \textbf{100\% on-time} reporting with consistent \textbf{8/10+} stakeholder satisfaction.

% ── Closing ─────────────────────────────────────────────────────────────────
I would welcome the chance to bring this experience to Westpac and to help embed best-practice analytics across the Financial Crime Detection function. Thank you for your time and consideration.

\vspace{14pt}

Warm regards,

\vspace{24pt}

\textbf{Quoc Anh Trinh (Andrew)}\\
+61 451 886 468\\
\href{mailto:andrews.trinh@gmail.com}{andrews.trinh@gmail.com}\\
\href{https://www.linkedin.com/in/qatrinh}{linkedin.com/in/qatrinh}

\end{document}
