\documentclass[11pt, a4paper]{article}

\usepackage[a4paper, top=2cm, bottom=2cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=blue
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{8pt}

\pagestyle{empty}

\begin{document}

% ── Header ──────────────────────────────────────────────────────────────────
\begin{center}
    {\LARGE \textbf{Quoc Anh Trinh (Andrew)}}\\[4pt]
    {\small
        +61 451 886 468 \quad|\quad
        \href{mailto:andrews.trinh@gmail.com}{andrews.trinh@gmail.com} \quad|\quad
        \href{https://www.linkedin.com/in/qatrinh}{linkedin.com/in/qatrinh}
    }
\end{center}

\vspace{4pt}
\hrule
\vspace{14pt}

% ── Date ────────────────────────────────────────────────────────────────────
\today

\vspace{8pt}

Hiring Manager\\
Network Transport Operations\\
Linfox

\vspace{10pt}

% ── Salutation ──────────────────────────────────────────────────────────────
Dear Hiring Manager,

% ── Opening ─────────────────────────────────────────────────────────────────
I am writing to express my strong interest in the \textbf{Data \& Analytical Lead} position at Linfox. With a background in leading intelligence functions and a Master of Business Analytics, I have professional experience in owning and optimising digital platforms that bridge the gap between complex data and operational value. I am particularly drawn to Linfox’s commitment to safety and efficiency, and the opportunity to lead the digital evolution of your Network Transport operations.

% ── Why Linfox & Role Fit ───────────────────────────────────────────────────
Linfox is synonymous with excellence in logistics across the Asia-Pacific. The "Data \& Analytical Lead" role resonates with my approach to analytics: treating data platforms as products that must be continuously improved and deeply embedded into Business-as-Usual (BAU) to drive real-world outcomes. I thrive at the intersection of operations and technology, ensuring that digital investments translate into measurable customer and operational value.

% ── Core experience tailored to Linfox ─────────────────────────────────────
In my current role at Bendigo \& Adelaide Bank, I lead the intelligence and analytics function within Financial Crime Risk. My experience closely aligns with the requirements of this role:

\textbf{Digital Product Ownership and BAU Embedding:}
I focus on the entire lifecycle of digital solutions, from initial requirement translation to post-implementation ownership. By establishing clear governance and ownership models for our analytics platforms, I have reduced ad-hoc reporting requests by 70\% and improved prioritisation efficiency by 60\%. This ensures that systems remain fit-for-purpose long after go-live.

\textbf{Translating Operational Needs into Backlogs:}
I act as the primary translator between operational stakeholders and technical delivery teams. I am adept at converting business pain points into prioritised digital backlogs, user stories, and technical requirements. This includes managing complex datasets and engineering automated workflows that reduced regulatory preparation time by 80\% --- achieved through rigorous change control and cross-functional collaboration.

\textbf{Platform Optimisation and Systems Exposure:}
I apply SQL, Python, and Power BI daily to build and sustain digital platforms. While my primary experience lies within financial services systems (including AWS and Azure ecosystems), I have a proven ability to quickly master new platforms. I understand the critical role systems like Blue Yonder and SAP play in transport operations and am eager to apply my technical rigour to Linfox’s digital freight and routing platforms.

\textbf{Stakeholder Partnering and Value Realisation:}
I partner closely with operational leaders, IT teams, and external vendors to track and measure the value of digital investments. Whether workshopping system outcomes with internal stakeholders or presenting data insights to external partners, I focus on building trust through transparent, high-quality data governance.

% ── Qualifications ───────────────────────────────────────────────────────────
I hold a \textbf{Master of Business Analytics from Deakin University}, which provides the theoretical foundation for my data-driven approach. My career has been defined by a passion for continuous improvement and a "product-style" mindset that prioritises availability, stability, and fitness for purpose.

% ── Closing ─────────────────────────────────────────────────────────────────
I am excited about the prospect of bringing my expertise in digital operations and data leadership to Linfox. I look forward to the possibility of discussing how I can help optimise your digital platforms and support the continued success of your Network Transport operations.

Thank you for your time and consideration.

\vspace{20pt}

Warm regards,

\vspace{30pt}

\textbf{Quoc Anh Trinh (Andrew)}\\
+61 451 886 468\\
\href{mailto:andrews.trinh@gmail.com}{andrews.trinh@gmail.com}\\
\href{https://www.linkedin.com/in/qatrinh}{linkedin.com/in/qatrinh}

\end{document}
