\documentclass[11pt, a4paper]{letter}

\usepackage[a4paper, top=1.5cm, bottom=1.5cm, left=2.2cm, right=2.2cm]{geometry}
\usepackage{fontenc}
\usepackage{inputenc}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{hyperref}
\usepackage{xcolor}

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=blue
}

% Remove default letter formatting
\setlength{\parindent}{0pt}
\setlength{\parskip}{5pt}

\begin{document}

% ── Header ──────────────────────────────────────────────────────────────────
\begin{center}
    {\LARGE \textbf{Quoc Anh Trinh (Andrew)}}\\[4pt]
    {\small
        +61 451 886 468 \quad|\quad
        \href{mailto:andrews.trinh@gmail.com}{andrews.trinh@gmail.com} \quad|\quad
        \href{https://www.linkedin.com/in/qatrinh}{linkedin.com/in/qatrinh}
    }
\end{center}

\vspace{6pt}
\hrule
\vspace{10pt}

% ── Date & Recipient ────────────────────────────────────────────────────────
\today

\vspace{8pt}

Hiring Manager\\
Forensic Data Analytics --- Forensic \& Integrity Services\\
EY Australia

\vspace{6pt}

% ── Salutation ──────────────────────────────────────────────────────────────
Dear Hiring Manager,

% ── Opening ─────────────────────────────────────────────────────────────────
I am writing to apply for the \textbf{Senior Consultant} role in EY's Forensic Data Analytics team. Over five years in Australian banking and FinTech --- currently leading the Intelligence and Analytics function within Financial Crime Risk at Bendigo \& Adelaide Bank --- I have spent my career doing exactly what this role is built around: leveraging data analytics to detect fraud, financial crime and anomalous behaviour, and translating complex datasets into evidence and insight that stakeholders can act on.

% ── Why EY ──────────────────────────────────────────────────────────────────
What draws me to EY's Forensic \& Integrity Services is the chance to put integrity at the heart of compliance work across a diverse portfolio of clients and industries --- moving from a single institution to the full life cycle of forensic data analysis, from discovery and capture through to analysis and client-ready reporting.

% ── Detection, algorithms and analytics ─────────────────────────────────────
\textbf{Detection, algorithms and analytics:}
I design SQL- and Python-driven analytics to surface irregular financial transactions and anomalous behaviour. Using statistical calibration and clustering on transaction monitoring models, I reduced false positives by up to \textbf{67\%}, removed \textbf{5{,}000+} unnecessary alerts and saved \textbf{300+} hours a year, while building automated daily workflows processing \textbf{150+} alerts at \textbf{99.9\%} integrity. I also build production machine learning, NLP and LLM solutions --- enforcement-action checkers and typology extractors on FastAPI with vector search --- to accelerate the fact-finding process.

% ── Data engineering and ETL ────────────────────────────────────────────────
\textbf{Data engineering and ETL:}
I extract, validate, transform and load high-volume structured and unstructured data from disparate sources, and engineered interim SQL monitoring that held \textbf{100\%} compliance continuity across \textbf{2M+} transactions during a platform exit. I work hands-on with SQL across commercial relational databases, Python and R, Spark/PySpark for big data, and AWS and GCP cloud platforms.

% ── Reporting, visualisation and communication ──────────────────────────────
\textbf{Reporting, visualisation and communication:}
I own the Power BI dashboards in our transaction monitoring product, eliminating \textbf{70\%} of ad-hoc requests and cutting prioritisation time by \textbf{60\%}, and co-designed an AI-driven regulatory reporting pipeline using LLMs, NLP, Python and SQL that cut preparation time by \textbf{80\%}. Communicating technical information in plain language is a strength I have deliberately built --- I have tutored over \textbf{100 students} in SQL and Python and regularly present data, conclusions and recommendations to non-technical stakeholders.

% ── Broader credentials ─────────────────────────────────────────────────────
Alongside my \textbf{Master of Business Analytics from Deakin University}, I am beginning a formal research journey on \textbf{AI for compliance}. My grounding in financial processes and regulatory reporting means I can hypothesise, analyse and draw conclusions from financial and operational data from day one.

% ── Closing ─────────────────────────────────────────────────────────────────
I would welcome the opportunity to discuss how my financial-crime analytics background can contribute to EY's Forensic Data Analytics team. My resume is attached, and I am available at your convenience.

Thank you for considering my application.

\vspace{6pt}

Warm regards,

\vspace{14pt}

\textbf{Quoc Anh Trinh (Andrew)}

\end{document}
