\documentclass[11pt, a4paper]{article}

\usepackage[a4paper, top=2cm, bottom=2cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=blue
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{8pt}

\pagestyle{empty}

\begin{document}

% ── Header ──────────────────────────────────────────────────────────────────
\begin{center}
    {\LARGE \textbf{Quoc Anh Trinh (Andrew)}}\\[4pt]
    {\small
        +61 451 886 468 \quad|\quad
        \href{mailto:andrews.trinh@gmail.com}{andrews.trinh@gmail.com} \quad|\quad
        \href{https://www.linkedin.com/in/qatrinh}{linkedin.com/in/qatrinh}
    }
\end{center}

\vspace{4pt}
\hrule
\vspace{14pt}

% ── Date ────────────────────────────────────────────────────────────────────
\today

\vspace{8pt}

Hiring Manager\\
AI Transformation Office\\
Qualitas Limited

\vspace{10pt}

% ── Salutation ──────────────────────────────────────────────────────────────
Dear Hiring Manager,

% ── Opening ─────────────────────────────────────────────────────────────────
I am writing to express my enthusiastic interest in joining the AI Transformation Office at Qualitas. As an experienced technical lead with a Master of Business Analytics and a proven track record in architecting production-grade AI solutions, I am inspired by Qualitas’s reputation as a leading alternative real estate investment manager. I thrive at the intersection of complex engineering and real-world business impact, and I am eager to help your team realise its vision for an AI-powered future.

% ── AI Engineering & Production Focus ───────────────────────────────────────
In my current role leading intelligence and analytics at Bendigo \& Adelaide Bank, I have spent over five years turning complex requirements into production-ready data and AI products. My background specifically aligns with your requirement for an engineer who "makes things work":

\textbf{Building and Deploying LLM Workflows:}
I have architected sophisticated Agentic AI solutions involving NLP and LLM pipelines to automate the extraction of insights from highly complex regulatory documents. My experience includes prompt engineering, RAG, and developing evaluation frameworks to ensure 99.9\% logic alignment. I am comfortable managing the full lifecycle of AI workloads—from Python API development using FastAPI to configuring robust guardrails and regression detection.

\textbf{Infrastructure and Integration Mastery:}
I have hands-on experience across major cloud ecosystems, including Azure infrastructure, and I am adept at building integrations via REST APIs and webhooks. I have designed and implemented ETL/ELT pipelines that reconcile data across systems while maintaining strict governance and security standards. Whether it is deploying Azure Functions or configuring low-code automations in Power Automate, I prioritise selecting the right tool for the specific business objective.

\textbf{Serving as a Bridge to the Business:}
I pride myself on being a technical specialist who speaks the language of the business. By translating complex process redesigns into technical requirements, I successfully automated regulated reporting workflows that reduced preparation time by 80\%. I am passionate about user adoption and regularly work directly with stakeholders during UAT to ensure that technical solutions land successfully and deliver measurable value.

% ── Why Qualitas & Sector Fit ───────────────────────────────────────────────
Qualitas’s position as an ASX-listed leader in real estate private credit requires a high-performance mindset and a strong focus on risk-adjusted outcomes. My background in financial crime risk has honed my attention to detail and my commitment to data privacy and ethical AI behaviour. I am eager to apply this rigour to Qualitas’s AI Transformation journey, supporting your investment teams with intelligent services that scale.

% ── Closing ─────────────────────────────────────────────────────────────────
I am ready to bring my "free-thinking" (to use your term) and technical depth to the Melbourne-based AI Transformation team. I look forward to the possibility of discussing how my experience in AI enablement and product-oriented engineering can support Qualitas's strategic goals.

Thank you for your time and consideration.

\vspace{20pt}

Warm regards,

\vspace{30pt}

\textbf{Quoc Anh Trinh (Andrew)}\\
+61 451 886 468\\
\href{mailto:andrews.trinh@gmail.com}{andrews.trinh@gmail.com}\\
\href{https://www.linkedin.com/in/qatrinh}{linkedin.com/in/qatrinh}

\end{document}
