\documentclass[11pt, a4paper]{article}

\usepackage[a4paper, top=2cm, bottom=2cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=blue
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{8pt}

\pagestyle{empty}

\begin{document}

% ── Header ──────────────────────────────────────────────────────────────────
\begin{center}
    {\LARGE \textbf{Quoc Anh Trinh (Andrew)}}\\[4pt]
    {\small
        +61 451 886 468 \quad|\quad
        \href{mailto:andrews.trinh@gmail.com}{andrews.trinh@gmail.com} \quad|\quad
        \href{https://www.linkedin.com/in/qatrinh}{linkedin.com/in/qatrinh}
    }
\end{center}

\vspace{4pt}
\hrule
\vspace{14pt}

% ── Date ────────────────────────────────────────────────────────────────────
\today

\vspace{8pt}

Recruitment Team\\
La Trobe University

\vspace{10pt}

% ── Salutation ──────────────────────────────────────────────────────────────
Dear Recruitment Team,

% ── Opening ─────────────────────────────────────────────────────────────────
I am writing to express my strong interest in the \textbf{Senior Analytics Specialist} position within the Marketing team at La Trobe University. With a Master of Business Analytics and over five years of experience leading data-driven functions—currently as the Lead of Intelligence and Analytics at Bendigo \& Adelaide Bank—I have a proven track record of designing reporting frameworks, analysing complex multi-source data, and translating insights into clear recommendations that optimise customer journeys.

% ── Why La Trobe University ─────────────────────────────────────────────────
I am drawn to La Trobe University's commitment to creating a diverse, inclusive, and safe community, as well as its strategic focus on leveraging digital touchpoints to enhance engagement and acquisition. The opportunity to work with the Manager of Customer Journey to shape data-led planning, personalisation, and testing aligns perfectly with my passion for using advanced analytics to improve user experiences across digital channels.

% ── Core experience tailored to Senior Analytics Specialist ─────────────────
In my current role, I manage the full data lifecycle for complex datasets, driving strategic initiatives and fostering cross-functional collaboration. My background directly supports the requirements of this role:

\textbf{Advanced Digital Analytics and Dashboards:}
I have extensive experience designing automated dashboards and reporting frameworks that provide actionable visibility into performance. By developing tools that ingest and transform millions of data points from diverse sources, I have enabled cross-functional teams to track key metrics reliably. I am adept at setting up performance reporting that connects digital channels (web, email, CRM) to the broader customer journey.

\textbf{Translating Insights for Non-Technical Audiences:}
A core part of my role is translating complex analytical findings into clear, decision-ready recommendations for non-technical stakeholders. Whether conducting segmentation analysis or evaluating funnel performance, I consistently partner with operational and marketing teams to ensure data directly informs targeting, strategy, and business outcomes.

\textbf{Data Governance and Quality Assurance:}
Coming from a highly regulated banking environment, I place a premium on data governance and quality assurance. I have built automated pipelines that ensure 99.9\% data integrity and am deeply familiar with privacy obligations and the importance of maintaining rigorous platform governance—essential for managing multi-channel marketing analytics.

\textbf{Testing, Optimisation, and Delivery:}
I am highly experienced in applying technical judgement to develop improved methods and solutions. From leading A/B testing initiatives to identifying measurement improvements, I excel at delivering multiple data priorities to tight deadlines while continuously optimising conversion paths.

% ── Closing ─────────────────────────────────────────────────────────────────
I am excited about the opportunity to bring my technical expertise in analytics, segmentation, and platform governance to La Trobe University, supporting your marketing activity and enhancing the prospective student journey. I look forward to the possibility of discussing how my skills and background can contribute to your team's success.

Thank you for your time and consideration.

\vspace{20pt}

Warm regards,

\vspace{30pt}

\textbf{Quoc Anh Trinh (Andrew)}\\
+61 451 886 468\\
\href{mailto:andrews.trinh@gmail.com}{andrews.trinh@gmail.com}\\
\href{https://www.linkedin.com/in/qatrinh}{linkedin.com/in/qatrinh}

\end{document}