\documentclass[11pt, a4paper]{article}

\usepackage[a4paper, top=2cm, bottom=2cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=blue
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{8pt}

\pagestyle{empty}

\begin{document}

% ── Header ──────────────────────────────────────────────────────────────────
\begin{center}
    {\LARGE \textbf{Quoc Anh Trinh (Andrew)}}\\[4pt]
    {\small
        +61 451 886 468 \quad|\quad
        \href{mailto:andrews.trinh@gmail.com}{andrews.trinh@gmail.com} \quad|\quad
        \href{https://www.linkedin.com/in/qatrinh}{linkedin.com/in/qatrinh}
    }
\end{center}

\vspace{4pt}
\hrule
\vspace{14pt}

% ── Title ────────────────────────────────────────────────────────────────────
\begin{center}
    {\Large \textbf{Response to Essential Criteria}}\\[4pt]
    {\large \textbf{Senior Analytics Specialist -- La Trobe University}}
\end{center}

\vspace{10pt}

% ── Criteria 1 ─────────────────────────────────────────────────────────────────
\textbf{1. Advanced proficiency in digital analytics platforms, reporting tools, dashboard design and marketing performance reporting frameworks.}

I have extensive hands-on experience designing and delivering automated dashboards, reporting frameworks, and data visualisations across both FinTech and banking environments. Over the past five years, I have architected and owned complex reporting tools using platforms such as Power BI, Metabase, and custom web-based UI streams. 

At Bendigo \& Adelaide Bank, I own the Power BI dashboards for the transaction monitoring product, developing reporting frameworks that track key operational metrics and guardrails. Previously, at Remitano, I led the delivery of marketing performance and operational analytics dashboards, which eliminated a large volume of ad-hoc requests and reduced prioritisation time by 60\%. My proficiency extends to the underlying data architecture, allowing me to build the data pipelines (using SQL, Python, BigQuery, dbt) that feed these digital analytics platforms, ensuring dashboards are both insightful and highly performant.

% ── Criteria 2 ─────────────────────────────────────────────────────────────────
\textbf{2. Strong understanding of digital marketing channels and the customer journey, including how data flows across web, paid media, email, SEO, CRM and social platforms.}

Through my work in marketing analytics at Remitano---an international cryptocurrency exchange with over \$500M+ in trading volume---I developed a deep understanding of how customer data flows across digital touchpoints. I was responsible for connecting data across various channels to build a cohesive view of the customer journey, from initial web interaction to user registration and ongoing engagement via CRM and email.

I have actively mapped data flows between customer relationship management platforms and operational databases to fuel targeted marketing efforts. For example, I modelled user acquisition and engagement data to optimise multi-tier referral programs, and I designed scalable solutions that integrated marketing campaign data to evaluate cross-channel performance. This experience ensures I can effectively track and measure the full customer lifecycle, connecting engagement metrics from various platforms into unified reporting.

% ── Criteria 3 ─────────────────────────────────────────────────────────────────
\textbf{3. Strong ability to analyse complex multi-source data, interpret digital marketing and customer journey performance, and translate insights into clear recommendations for non-technical audiences.}

Translating complex data from disparate sources into actionable, business-ready insights is a core strength of my current and previous roles. I regularly ingest data from diverse systems---such as web activity, CRM logs, and transactional databases---and run advanced statistical analyses using SQL and Python.

At Bendigo \& Adelaide Bank, I analyse millions of transaction records alongside internal reports, applying statistical and machine learning techniques to optimise detection scenarios. Crucially, I translate these highly technical findings into clear recommendations for non-technical stakeholders in operations, compliance, and governance. Whether I am presenting the results of A/B tests, explaining segmentation models, or providing regular marketing funnel performance updates as I did at Remitano, I focus on delivering insights that empower operational teams to make strategic, data-led decisions with confidence.

% ── Criteria 4 ─────────────────────────────────────────────────────────────────
\textbf{4. Experience with segmentation, testing, attribution, conversion optimisation, data governance, privacy obligations, stakeholder management and delivery of multiple priorities to tight deadlines.}

My background directly covers the full spectrum of advanced analytics requirements. 
\begin{itemize}
    \item \textbf{Segmentation and Testing:} At Remitano, I built customer classification models using Python and SQL to automate email marketing, which successfully drove a 30\% uplift in click-through rates. I frequently conduct A/B testing and apply statistical confidence testing to evaluate model performance and identify optimisations.
    \item \textbf{Data Governance and Privacy:} Operating in highly regulated financial environments (Bendigo \& Adelaide Bank), I place a strong emphasis on data governance. I engineer pipelines that ensure 99.9\% data integrity, incorporate strict data masking/rehydration protocols for privacy compliance, and build robust automated workflows to maintain platform governance.
    \item \textbf{Stakeholder Management and Delivery:} I own analytics functions serving diverse cross-functional teams. I am accustomed to managing multiple, high-priority strategic initiatives---such as migrating complex data models during bank mergers or automating regulatory reporting pipelines---while consistently delivering accurate results to tight deadlines.
\end{itemize}

\end{document}