\documentclass[11pt, a4paper]{article}

\usepackage[a4paper, top=2cm, bottom=2cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=blue
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}

\pagestyle{empty}

\begin{document}

% ── Header ──────────────────────────────────────────────────────────────────
\begin{center}
    {\LARGE \textbf{Quoc Anh Trinh (Andrew)}}\\[4pt]
    {\small
        +61 451 886 468 \quad|\quad
        \href{mailto:andrews.trinh@gmail.com}{andrews.trinh@gmail.com} \quad|\quad
        \href{https://www.linkedin.com/in/qatrinh}{linkedin.com/in/qatrinh}
    }
\end{center}

\vspace{4pt}
\hrule
\vspace{14pt}

% ── Date ────────────────────────────────────────────────────────────────────
\today

\vspace{8pt}

Hiring Manager / Panel\\
Financial Crime Solutions\\
Bendigo and Adelaide Bank

\vspace{10pt}

% ── Salutation ──────────────────────────────────────────────────────────────
Dear Hiring Manager / Panel,

% ── Opening ─────────────────────────────────────────────────────────────────
AUSTRAC's reformed regime has shifted the question from ``do we have controls?'' to ``do our controls demonstrably work?'' Meeting that standard requires financial crime capability that is measurable, auditable, and continuously improving --- and delivery leadership that can turn that agenda into working, evidenced solutions while growing the analysts who sustain them. That is what I am applying to do, and it is the work I have already been doing at Bendigo and Adelaide Bank for the past five years.

% ── Delivery record ───────────────────────────────────────────────────────────
My delivery record in the Bank's intelligence and analytics function spans detection, automation, and insight. In the 2025 scenario development program I coordinated the build of \textbf{nine new} detection scenarios --- personally delivering \textbf{three} with a statistically significant true positive uplift while supporting colleagues on design and calibration --- and in the annual rule reviews I peer-reviewed and assisted team members through statistical testing and recalibration. On automation, I co-delivered the AI-driven UAR-to-SMR pipeline that cut regulatory reporting preparation time by \textbf{80\%}, and stood up a full detection service from scratch within \textbf{2--3 days} to maintain uninterrupted monitoring coverage during an urgent brand transition. On insight, I have delivered dashboards that give the Bank new lines of sight --- including a SWIFT payment network graph for cross-border analysis and outlier detection of abnormal transaction volumes and values.

% ── Working style ──────────────────────────────────────────────────────────
That mix of delivering and supporting reflects how I work: build the reasoning behind the work, not hand over answers --- and I am equally comfortable working to a direction set above me, translating priorities from senior leadership into scoped, testable deliverables with clear evidence of effectiveness.

% ── Vision for the role ──────────────────────────────────────────────────────
Where I would focus as Manager is the next layer of capability. First, \textbf{people}: developing analysts who can own detection design end to end, so capability persists beyond any single project or platform. Second, applying \textbf{quantitative methods and machine learning} extensively across our solutions --- for example, a recommendation-style prioritisation model that ranks alerts by the likelihood of a reportable outcome, extending our abnormal value and volume monitoring into systematic outlier detection, and enriching the SWIFT network graph with NPP and other payment data as a foundation for graph-based detection --- applying methods such as dense-flow subgraph search (FlowScope, Li et al., 2020) and temporal graph networks for financial anomaly detection (Kim et al., 2024) to surface flow patterns that isolated transaction rules miss. Third, engineering and leading \textbf{sustainable AI with proper guardrails} --- proven in practice by drafting grounds-for-suspicion narratives through an LLM pipeline on masked data, and deepened through Claude Architect training in AI engineering, my proposed MPhil in AI for AML/CTF reasoning, and applied builds such as the Typology Extractor. The natural extension is end-to-end automation of the SMR creation stream: an agentic pipeline built on Anthropic's agent-design principles and informed by published agentic SAR frameworks (Co-Investigator AI, 2025), connecting case consolidation, narrative drafting, and compliance validation --- with analyst review retained as the final control. Fourth, sharper \textbf{build-versus-buy}: benchmarking vendor capability against internal baselines so the Bank extracts full value from its platform investments. Each of these I can bring to senior leadership as costed, testable proposals.

% ── Closing ─────────────────────────────────────────────────────────────────
I would welcome the opportunity to discuss how I can help lead the Bank's next phase of financial crime capability.

\vspace{14pt}

Yours sincerely,

\vspace{24pt}

\textbf{Quoc Anh Trinh (Andrew)}\\
+61 451 886 468\\
\href{mailto:andrews.trinh@gmail.com}{andrews.trinh@gmail.com}\\
\href{https://www.linkedin.com/in/qatrinh}{linkedin.com/in/qatrinh}

\end{document}
