\documentclass[11pt, a4paper]{article}

\usepackage[a4paper, top=2cm, bottom=2cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=blue
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{8pt}

\pagestyle{empty}

\begin{document}

% ── Header ──────────────────────────────────────────────────────────────────
\begin{center}
    {\LARGE \textbf{Quoc Anh Trinh (Andrew)}}\\[4pt]
    {\small
        +61 451 886 468 \quad|\quad
        \href{mailto:andrews.trinh@gmail.com}{andrews.trinh@gmail.com} \quad|\quad
        \href{https://www.linkedin.com/in/qatrinh}{linkedin.com/in/qatrinh}
    }
\end{center}

\vspace{4pt}
\hrule
\vspace{14pt}

% ── Date ────────────────────────────────────────────────────────────────────
\today

\vspace{8pt}

Hiring Manager\\
KPMG Forensic team\\
KPMG Australia

\vspace{10pt}

% ── Salutation ──────────────────────────────────────────────────────────────
Dear Hiring Manager,

% ── Opening ─────────────────────────────────────────────────────────────────
I am writing to express my strong interest in the \textbf{Forensic Data Analytics Senior Consultant} (Wage Compliance) position within KPMG’s Forensic team. With a Master of Business Analytics and a background in financial crime analytics within Australian banking, I am a data-driven professional who thrives on using precision to uphold ethical business practices. I am particularly drawn to KPMG’s mission of helping workers receive their fair entitlements through rigorous data investigation and remediation.

% ── Why KPMG Forensic ──────────────────────────────────────────────────────
KPMG’s Forensic team is renowned for its technical excellence in responding to complex financial crime issues. The transition from detecting fraud and money laundering to uncovering wage underpayment is a natural progression for my skillset. I believe that forensic analytics is most impactful when it protects individuals and ensures regulatory compliance, and I am excited by the prospect of joining a team where precision directly translates into fairness for workers across Australia.

% ── Core experience tailored to Forensic Analytics ─────────────────────────
In my current role as Lead of Intelligence and Analytics in the Financial Crime Risk unit at Bendigo \& Adelaide Bank, I have developed a forensic mindset for identifying discrepancies and non-compliant behaviours:

\textbf{Investigation of Complex Administrative Data:}
I have extensive experience analysing large, complex datasets to identify anomalies and regulatory breaches. I led the establishment of an interim monitoring function that maintained 100\% continuity across 2M+ transactions, requiring the same level of attention to detail and data quality review that wage compliance requires across payroll and time \& attendance systems.

\textbf{Logic-Driven Model Development:}
I am an expert in translating complex regulatory requirements—such as AML/CTF Acts—into robust SQL and Python-based identification models. This experience is directly transferable to the creation of calculation models for Modern Awards, Enterprise Agreements, and National Employment Standards. I pride myself on maintaining 99.9\% data integrity across all my analytical workflows, ensuring that findings are defendable and accurate.

\textbf{Stakeholder Reporting and Communication:}
I excel at translating complex technical findings into clear, executive-ready briefings. Whether delivering ongoing monitoring dashboards in Power BI or reporting on remediation matters, I focus on providing decision-ready advice that supports both ethical business practices and legal requirements. My background in professional services and banking has honed my ability to work within diverse teams of subject matter specialists.

\textbf{Technical Versatility:}
My primary technical stack includes advanced SQL and Python, and I am a fast learner when it comes to tools like Alteryx or specific payroll software. I am committed to continuous learning and am eager to apply my analytical rigour to the specific challenges of payroll forensic investigation and cost modelling for Enterprise Agreements.

% ── Closing ─────────────────────────────────────────────────────────────────
I am passionate about using my analytical capabilities for social good, and I am eager to contribute to KPMG’s wage compliance remediation efforts. I look forward to discussing how my experience in financial crime forensics and large-scale data modelling can help your team protect workers' rights and support your clients.

Thank you for your time and consideration.

\vspace{20pt}

Warm regards,

\vspace{30pt}

\textbf{Quoc Anh Trinh (Andrew)}\\
+61 451 886 468\\
\href{mailto:andrews.trinh@gmail.com}{andrews.trinh@gmail.com}\\
\href{https://www.linkedin.com/in/qatrinh}{linkedin.com/in/qatrinh}

\end{document}
